%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[russian]{babel} 
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Mark Kashirskii}} & Email : \href{mailto:marshelo44@gmail.com}{marshelo44@gmail.com}\\
  \href{https://novosibirsk.hh.ru/resume/7dd6bcc0ff09c0c58a0039ed1f4263354f6d6c}{HH: https://novosibirsk.hh.ru/resume/7dd6bcc0ff09c0c58a0039ed1f4263354f6d6c} & Mobile : +7-983-186-7773 \\
  \href{https://github.com/mariklolik}{Github: https://github.com/mariklolik} \\
  \href{https://t.me/mariklolik}{Telegram: https://t.me/mariklolik}\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Yandex Lyceum}{Barnaul, Russia}
      {Industrial programming on python ;  Golden certificate of excellence}{Sep 2017 - Aug 2019}
       \resumeItemListStart
	    \resumeItem {Backend}{Libraries: Flask, Django}
        \resumeItem {Data storage and processing libraries}{SQLalchemy, MySQL, SQL language}
        \resumeItem {Frontend}{SASS, Haml, Bootstrap}
        \resumeItem {Rich experience in REST-Api development}{}
        \resumeItem {Interfaces}{QT, Kivy}
        \resumeItemListEnd
        
        \resumeSubheading
        {MIPT Deep Learning School}{Moscow, Russia}
      {Machine Learning and data processing on python ;  Bronze certificate of excellence}{Sep 2018 - Aug 2020}
       \resumeItemListStart
	    \resumeItem {Data visualization}{Seaborn}
        \resumeItem {Data preprocessing}{Pandas}
        \resumeItem {Machine learning}{Keras, Tensorflow, Scikit-Learn}
        \resumeItemListEnd

        \resumeSubheading
        {Yandex Backend Development School}{Yandex, Remote}
      {Backend Development and testing on python, DevOps/Deploy; }{Sep 2022 - Dec 2022}
       \resumeItemListStart
	    \resumeItem {Backend Development}{FastAPI, Tornado, Flask, Architecture of distributed systems, microservices}
        \resumeItem {DevOps and Databases}{ Docker compose, uvicorn, optimizations, Migrations, Advanced indexing, Architecture planning. Implementations via postgres, Redis, MongoDB}
        \resumeItem {Testing}{Highload, stress, soak and volume testing, Debug logging}
        \resumeItemListEnd
        
    \resumeSubheading
     {Novosibirsk State University}{Novosibirsk, Russia}
      {Software engineering ;  GPA: 4.0}{Aug 2021 - Aug 2025}
      
	   {\scriptsize \textit{Courses: Algebra and geometry,Informatics, Mathematical analysis, Mathematical logic and theory of algorithms, Programming, Digital circuitry, Discrete math, Math statistics, Probability theory}}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{C++, Python, Java, C, SQL, Unix scripting}
    \resumeSubItem{Frameworks and Libraries}{Flask, Django, Tornado, FastAPI, pytest, alembic, SqlAlchemy}
	\resumeSubItem{Tools}{Docker, GIT, Matlab, Postgres, Redis, MongoDB, Yandex Cloud, Yandex Tank}
\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Yandex Lyceum}{Barnaul, Russia}
    {Pet-Projects}{}
    \resumeItemList
        \resumeItem{Flask Web project}
          {Developed the news aggregator website. The site shows my fullstack-development skills. The frontend uses HTML, HAML, SCSS, Bootstrap and Flask-Blueprints technology. Backend is developed on Flask.
          Connection to ORM database is realized with python framework SQLAlchemy.\
        The project supports registration and login-in with your email. If you are registred as an author you are able to write posts accompanied with pictures and videos, HTML-tag them, subscribe and rate other users posts.
        If you are a user then you are able to like news, subscribe authors and write HTML-tagged posts.}\\
        \href{https://github.com/mariklolik/stpj}{Project github: https://github.com/mariklolik/stpj}
          \resumeItem{PyQt REST-Api project}
          {Designed and developed a desktop-app to interact with Yandex-Maps Api. Solution allows you to expand standard functionality of Yandex-Maps with your own scripts (ex. advanced path-finding through many points, algorithmic drawing on map, expanding area map with terrain info).
          Your own GIS-scripts mustn't be written in programming language. Interface solution allow you develop and save scripts with script-blocks that will be interpreted with a special programming language developed for this project.}
          \resumeItem{Weather tracking app}{Designed and developed a PyQt-app to help users understand what to wear today. User adds to database the clothes that he has in his wardrobe and style and temperature preferences. The app tracks the weather outside and send you either sms nor email what to wear today. The weather info is received from OpenWeatherMap-api.}
          \resumeItem{Yandex-Alice game}{Developed a game for Yandex-Alice smart assistant. The game itself reminds of action-verbs game. You say a city name to Alice then your voice is processed into text, server takes the last letter of the word and say you another city whose name begins with that letter. In development I used Yandex-Alice api and SQLAlchemy to save user score and create a leaderboard.}
          \resumeItem{Telgram, Discord, VK bots}{Developed different bots to simplify bussines interaction with potential users. }
          \resumeItem{UNIX-based systems administration}{Developed bash scripts to interact with linux file system. Taken a special course about a Linux Kernel}{}
          
      \resumeItemListEnd
      
    \resumeSubheading
    {Yandex Backend Development School }{Yandex, Remote}
    {}{}
    \resumeItem{Url-shortener application}{Designed and developed application. 
    Architectured app with OpenAPI, as a part of task studied business-analytics to increase percentage of people using app. App uses FastAPI and uvicorn. Sqlalchemy with alembic for DB and migrations }{}

    \resumeItem{Designing and integrating microservice app}{Studied a huge project of a pharmacy shop and developed a part of API to check the shopping bag. Api developed with Flask, DB is postgre}{}

    \resumeItem{Working with DataBases}{Done migrations of a huge database via Alembic, created indices to increase speed of search}{}

    \resumeItem{Testing}{Studied Unit, Integration and System testing. Implemented them via PyTest. Worked with Yandex Tank for highload testing}{}
      
    \resumeSubheading
		{Novosibirsk State University}{Novosibirsk, Russia}
		{First course programming}{Aug 2021 -  August 2022}
		\resumeItemListStart
        \resumeItem{C Language}
          {Worked on algorithms, studied at first course of university. Such as numerical systems calculator, Boyer-Moore algorithm, Huffman encoder, Graph algorithms and others. Developed tests for automatic testing system, constructed CMake-files. All algorihms are implemented in C language.}{}

        \resumeItem{C++ Language}
          {Studied OOP concepts. Used them to do the following tasks:
          designing and implementing Linked HashSet data structure, 
          creating Forth(programming language) interpreter, 
          developing smart-pointers. Worked with STL}{}
		\resumeItemListEnd

    
    \resumeItemListEnd
\resumeSubHeadingListEnd


\end{description}
%-------------------------------------------
\end{document}
